Pulmonary rehabilitation Robot Follower

### 2020-02-14 alpibot.tex
Upload a new version of this paper based on the ALPI bot solution.

\author{Luciano Bianchi, Esteban Buzniak, Rodrigo~Ramele,~\IEEEmembership{Member,~IEEE,}
        and~Juan~Miguel~Santos% <-this % stops a space
\thanks{R. Ramele  and J.M.Santos are with the Department
of  Computer Engineering, Instituto Tecn{o'}gico de Buenos Aires (ITBA), Ciudad de Buenos Aires,  Argentina e-mail: rramele@itba.edu.ar}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}

\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
robotics, tethered, HOT, COPD
\end{IEEEkeywords}

@@

Describe the PVC factoring process that Esteban created.  The materials and the name of the CNC that they are using to manufacture everything.  Add the components.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=8cm]{performance.eps}
\caption{Performance curves for the eight subjects included in the dataset of ALS patients.  Three out of eight subjects achieved the necessary performance to implement a valid P300 speller.}
\label{fig:performance}
\end{figure}

\begin{figure*}[!t]
\centering
\subfloat[Case I]{\includegraphics[width=15cm]{subject.png}\label{subject8}}
\caption{Ten sample P300 template patches for subjects 8 (A) and 3 (B) of the ALS Dataset.  Downward deflection is positive polarity. The P300 signature waveform is more clearly and consistent characterized for subject 8, whereas for subject 3 the characteristic patterns is more difficult to spot. }
\label{fig:p300templates}
\end{figure*}

@@

>>>>

\author{Bianchi Luciano, Buzniak Esteban, Ramele~Rodrigo,~\IEEEmembership{Member,~IEEE,}
        and Santos~Juan~Miguel% <-this % stops a space
\thanks{R. Ramele  and J.M.Santos are with the Department
of  Computer Engineering, Instituto Tecn{o'}gico de Buenos Aires (ITBA), Ciudad de Buenos Aires,  Argentina e-mail: rramele@itba.edu.ar}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Patients that suffer Chronic Obstructive Pulmonary Disease (COPD) underwent a procedure called Pulmonary Rehabilitation that helps them to improve disease prognosis.  During Pulmonary Rehabilitation procedures patients require external oxygen assistance.  The oxygen tank cannot be carried by the patient and some external assistance is required.   In this work a basic robot follower is proposed to carry the oxygen tank based on a differential tethered scheme.  Two algorithms are proposed in a very basic configuration.  BLABLABLABLABLABLA
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
robotics, tethered, COPD
\end{IEEEkeywords}

@@

Describe the PVC manufacturing process that Esteban created.  The materials and the name of the CNC that they are using to manufacture everything.  Add the components.

@@

The purpose of this section is to evaluate the feasibility of both control strategies, their engineering issues.

\begin{figure}[h!]
\centering
\includegraphics[width=8cm]{images/alpibot1.jpg}
\caption{This robot prototype.}
\label{fig:performance}
\end{figure}

\begin{figure*}[!t]
\centering
\subfloat[Case I]{\includegraphics[width=15cm]{images/alpibot2.jpg}\label{subject8}}
\caption{Ten sample P300 template patches for subjects 8 (A) and 3 (B) of the ALS Dataset.  Downward deflection is positive polarity. The P300 signature waveform is more clearly and consistent characterized for subject 8, whereas for subject 3 the characteristic patterns is more difficult to spot. }
\label{fig:p300templates}
\end{figure*}

@@

\subsection{Cliical Assesment} 
\label{section:assesment}
